---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.org/SimmonsBI/bmotif.svg?branch=master)](https://travis-ci.org/SimmonsBI/bmotif)
[![codecov](https://codecov.io/gh/SimmonsBI/bmotif/branch/master/graph/badge.svg)](https://codecov.io/gh/SimmonsBI/bmotif)

## Overview

`bmotif` is software to count occurrences of motifs in bipartite networks, as well as the number of times each node appears in each unique position within motifs. As well as R, it is available in [MATLAB](https://github.com/SimmonsBI/bmotif-matlab) and [Python](https://github.com/SimmonsBI/bmotif-python). `bmotif` was originally developed to analyse bipartite species interaction networks in ecology but its methods are general and can be applied to any bipartite graph.

## Installation

To install the released version from CRAN:

```{r, eval = FALSE}
install.packages("bmotif")
```

To install the development version from GitHub:

```{r, eval = FALSE}
install.packages("devtools") # install the devtools package
devtools::install_github("SimmonsBI/bmotif") # install bmotif
```

## Use

`bmotif` considers all 44 unique bipartite motifs up to six nodes. Within these motifs there are 148 unique positions.

`bmotif` has two functions: `mcount` and `positions`. `mcount` counts occurrences of motifs in a bipartite network. `positions` counts the number of times each node in a network occurs in each of the positions within the motifs.

The motifs corresponding to each motif ID and the positions corresponding to each motif position ID can be found in **Simmons, B. I., Sweering, M. J. M., Dicks, L. V., Sutherland, W. J. and Di Clemente, R. bmotif: a package for counting motifs in bipartite networks. bioRxiv. doi: 10.1101/302356**. These were defined following Baker et al (2015) Appendix 1 Figure A27.

## License
The code is released under the MIT license (see LICENSE file).

## Citation
If you use the package in your work, please cite:
Simmons, B. I., Sweering, M. J. M., Dicks, L. V., Sutherland, W. J. and Di Clemente, R. bmotif: a package for counting motifs in bipartite networks. bioRxiv. doi: 10.1101/302356

## References
Baker, N.J., Kaartinen, R., Roslin, T. and Stouffer, D.B., 2015. Species’ roles in food webs show fidelity across a highly variable oak forest. Ecography, 38(2), pp.130-139.

